\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.775in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\inDescItem}[1]{
 \item\small{
   {#1\vspace{-3pt}}
 }
}

\newcommand{\inDescListStart}{\begin{itemize}[leftmargin=*]\vspace{-3pt}}
\newcommand{\inDescListEnd}{\end{itemize}\vspace{-8pt}}


\newcommand{\resumeAltSubheading}[4]{
  \vspace{5.5pt}
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}

}

\newcommand{\projectItem}[3]{
    \inDescItem{\textbf{\href{#1}{#2\linkicon}}: #3}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label={}, leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\linkicon}{ \small\faicon{link}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/askarovich/}{\Large Yernazar Karabayev}} &  
  \href{https://www.linkedin.com/in/askarovich/}{askarovich \faicon{linkedin}}\\
  \href{mailto:soundsnick@gmail.com}{soundsnick@gmail.com} &
  \href{https://github.com/soundsnick}{soundsnick \faicon{github}}
\end{tabular*}



%-----------EXPERIENCE-----------------

\section{Experience}\vspace{-5pt}
  \resumeAltSubheading
  {\href{https://sber.kz/}{Sber Kazakhstan\linkicon}}
      {Almaty, Kazakhstan}
      {Lead Frontend Developer: \textbf{Internal infrastructure}}
      {February 2022 - Present}
    \inDescListStart
        \inDescItem{Implementing a microfrontend for the entire internal banking system projects.}
            \inDescListStart
                \inDescItem{Adjusted the whole architecture from zero. Monorepo with design-system}
                \inDescItem{Used Webpack 5 with its module federation, lerna, Storybook UI, React v18}
            \inDescListEnd
        \inDescItem{Mentored other developers, adjusted whole frontend team development workflow, code review.}
   \inDescListEnd
  
  \resumeAltSubheading
  {\href{https://incraft.org/}{InCraft/Bilim Media Group}}
  {Almaty, Kazakhstan}
  {Frontend developer: \textbf{Accounting platform}}
  {Feb 2021 - Aug 2021}
    \inDescListStart
        \inDescItem{Built an accounting system for educational organizations. }
            \inDescListStart
                \inDescItem{Implemented a design system, for flexible development/testing of a components.}
                \inDescItem{Came in with fresh views and approaches, made them work. Mentored other developers}
                \inDescItem{Used React, Storybook UI, Webpack.}
            \inDescListEnd
   \inDescListEnd
 
  \resumeAltSubheading
    {\href{https://alabs.team}{Azimut Labs\linkicon}}
    {Almaty, Kazakhstan}
    {Frontend Developer: \textbf{Tele2 and Altel projects}}
    {June 2020 - Dec 2020}
    \inDescListStart
        \inDescItem{Design system.}
            \inDescListStart
                \inDescItem{Implemented a number of components for design-system.}
                \inDescItem{Used React, Typescript, EmotionJs, ESLint.}
            \inDescListEnd
        \inDescItem{Implemented several pages integrated with Backend.}
            \inDescListStart
                \inDescItem{Got into server-side rendering approach of web-application development.}
                \inDescItem{Used React, NextJS, Typescript, EmotionJs, GraphQL with Apollo.}
            \inDescListEnd
   \inDescListEnd
   
  \resumeAltSubheading
    {\href{https://xn----7sbbb7bbx7alc6h.xn--p1ai/}{ Krasnodar Web-studio\linkicon}}
    {Krasnodar, Russia}
    {Fullstack developer: \textbf{Freelance}}
    {Feb 2015 - May 2019}
    \inDescListStart
        \inDescItem{Worked on a several projects.}
            \inDescListStart
                \inDescItem{Developed a number of websites for a clients.}
                \inDescItem{Used Ruby on Rails, Golang, PHP.}
            \inDescListEnd
   \inDescListEnd

%-----------ACHIEVEMENTS-----------------

\section{Achievements}\vspace{-4pt}
    \resumeAltSubheading
    {Hackday 2018 Participant}
    {Almaty, Kazakhstan}
    {Hackday}
    {December 2018}
     \inDescListStart
        \inDescItem{Created an MVP of professor ranking system on Ruby on Rails and VueJs. Integrated with an University education management system}
      \inDescListEnd
      
    \resumeAltSubheading
    {HackNU 2021 2nd place winner}
    {Almaty, Kazakhstan}
    {HackNU}
    {December 2018}
     \inDescListStart
        \inDescItem{Created frontend for ML based system for detecting student talents, then matching appropriate professions for him, and sharing an information about universities to applicate}
      \inDescListEnd


%-----------PROJECTS-----------------
\section{Projects}
 \inDescListStart
  \projectItem{OnBoarding.kz [in-progress]}{Building a platform for an automation of the new employee onboarding process.}
  \projectItem{https://ifkz.org}{ifkz.org}{Web resource accessibility checking platform. Used React/Vue, Ruby on Rails, Golang, Docker}
 
 \inDescListEnd
  \resumeSubHeadingListStart
  \resumeSubItem{\href{}{\color{blue}}}
      {}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------

\section{Education}\vspace{-4pt}
  \resumeAltSubheading
  {International IT University}
  {Almaty, Kazakhstan}
  {Unfinished Bachelor of Science in Computer Science;}
  {September. 2018 -- March. 2022}


%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \inDescListStart
    \inDescItem{
     \textbf{Languages}{: JS/TS, Golang, Ruby, HTML, CSS}
    }
    \inDescItem{
    \textbf{Technologies}{: React, Vue, NextJS, Webpack, babel, lerna, Storybook UI, Sass/Scss, EmotionJs/styled components, PostgreSQL/MySQL, MongoDB, Docker/Docker compose, Linux, Postman}}
 \inDescListEnd


%-------------------------------------------
\end{document}
